\documentclass[margin,line]{res}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

%\usepackage{helvet}
%\renewcommand{\sfdefault}{phv}
%\renewcommand{\familydefault}{\sfdefault}

\topmargin -.75in
\textheight 10.25in

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.25in
\itemsep=0in
\parsep=0in

\newcommand{\sstyle}{\sc}
\newenvironment{clist}{
  \begin{list}{$\bullet$}{
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in}
      \setlength{\topsep}{0in}
      \setlength{\leftmargin}{0.2in}}}
  {\end{list}}

\begin{document}
\name{Jason Cheok Wan \vspace*{.1in}}
\begin{resume}
%  \section{\sstyle Contact Information}
  {\small
  \vspace*{-.1in}
  \hspace*{-1.3in}jasonwan415@gmail.com \hfill 439 Topaz Terrace, Sunnyvale, CA 94089, USA\\
  \hspace*{-1.3in}\hfill (415) 900-9941}

  \vspace*{-.1in}
  \section{\sstyle Objective}
  A software engineering and leadership opportunity where I can contribute to
  building cool, elegant, and massively scaled products and businesses that
  matter to people.

  \section{\sstyle Summary of Qualifications}
  \begin{itemize}
  \item Thrived in multiple fast-paced startups as the first or one of the early
        engineers. Have a proven track record of leading and owning mission
        critical projects and features. Truly moved the needle to the success of
        these businesses.
  \item Versatile and nimble with a diverse set of software engineering and
        product skills. Have experience building cloud-based big-data analytics
        platform to enterprise SaaS and mobile applications from the ground up.
  \item Strong computer science background and passionate in technology and
        entrepreneurship. Analytical minded with great intuition and vision.
        Able to take on complex problems and directives with little guidance
        and take initiatives even when no one is asking.
  \item Team player, humble, always strive for the common goal. Have success
        leading cross-functional efforts and ready to inspire and be inspired by
        people of all ranks.
%  \item Quick learner and open-minded to new technologies. Motivated to tackle
%        new challenges. Eager to grow and be inspired by innovative ideas and
%        elegant approaches.
%  \item Good analytical skill and scrutiny on details enable me to prevent,
%        isolate, or actively tackling problems.
%  \item Generalist with a wide spectrum of computer science and software
%        engineering knowledge.
%  \item Strive for elegant, clean, and scalable solutions while getting
%        the job done.
%  \item Enjoy working in groups where effective communications and
%        practical opinions and criticisms are observed.
%  \item Passionate and enthusiastic for working in the field of computing.
  \end{itemize}

  \section{\sstyle Education}
  {\bf University of California, Berkeley}\\
  {\bf B.S. in Electrical Engineering and Computer Science} \hfill May 2010

  \section{\sstyle Professional Experience}
  {\bf Principal Software Engineer -- Nyansa Inc}, Palo Alto, CA USA\hfill Aug 2014 -- Present
  \vspace{.05in}
  \begin{itemize}
  \item First employee and engineer, an integral member who wore many hats and
        helped grow the company (SaaS with network data analytics) from Seed to
        Series B, from 0 to more than 70 customers.
  \item As a core full-stack engineer, led and delivered numerous mission
        critical features on a cloud-based big-data analytics product with
        Ruby on Rails, AngularJS, D3.js, Elasticsearch, MongoDB etc. Bringing
        product ideas to life with unique data visualizations.
  \item As the key data engineer, built and scaled distributed data pipelines
        using Scala and Apache Spark on a 280 cores cluster which processes over
        100,000 events per second, ingesting more than 2GB of data per minute
        from Kafka and Cassandra. Formulated an in-house Scala ecosystem and a
        sharable codebase that powers streaming and batch Spark applications,
        a data and analytics API exposed in GraphQL, and an interactive notebook
        for data science explorations with SparkSQL and Apache Zeppelin.
  \item Owned many of the architecture and feature designs. The person with the
        most extensive work and knowledge throughout the entire stack. Goto
        person for data modeling, queries generation, and cross-functional
        design and implementation decisions.
  \item Introduced the use of Elasticsearch as the main database for search and
        interactive analytics to the company which became the backbone of many
        critical product features. Established myself as the in-house guru.
        Showed lots of initiatives in bringing new technology and innovation to
        engineering and the product.
  \item Conducted numerous interviews, helped lead and expand the engineering
        team and mentor new members. Provided valuable insights to the general
        strategy of the company.
  \end{itemize}

  {\bf Lead Mobile Engineer -- Nbition Development Limited}, Hong Kong\hfill Nov 2013 -- Apr 2014
  \vspace{.05in}
  \begin{itemize}
  \item First employee and engineer. Solo built the Garffee iOS app from scratch
        to demonstrate a ``Smart-Cafe'' idea which earned acclaims and fundings
        from the Hong Kong government.
        % The app allows user to pre-order on the go and feeds location tracking
        % data to the order scheduling backend to eliminate waiting in line and
        % ensure a smooth and fresh pickup at store.
  \item Handled every aspect of building a production level iOS client against a
        REST backend and Facebook authentication and API integration. Owned the
        MVC design and wrote in quick iterations everything from UI, animations,
        to networking, data modeling, persistence, and unit-testing.
  \item Prototyped a feature for fingerprinting high-frequency sound waves with
        Fast Fourier Transform to serve as an unique solution to the indoor
        positioning problem.
  % \item Displayed a heart for quality by taking ownership and initiatives to
  %       deliver a user experience driven product with many subtle details and
  %       animations addressed.
  \end{itemize}

  \vspace{.5in}
  {\bf Senior Software Engineer -- Divide Inc (acq. Google 2014)}, Hong Kong\hfill Nov 2012 -- Nov 2013
  \vspace{.05in}
  \begin{itemize}
  \item Core developer of the Divide iOS client - a secure and isolated BYOD
        container for any business data residing on personal devices. Work
        encompasses a wide scope of the iOS stack from UI to runtime
        functions hooking. Also contributed to components such as the Exchange
        mail sync engine, mail parser, and VPN. Pushing the limits of iOS
        enterprise functionality and improved the overall product quality.
  \item Developed a core FIPS-compliant Public Key Infrastructure library shared
        between Android and iOS using C/C++ and OpenSSL. It forms the basis of
        the S/MIME mail feature which I also implemented on the iOS side.
  \item Led and managed a team of 4 developers on both Android and iOS for the
        Divide Files feature - a file manager for storing mail attachments and
        cloud-storage files securely and sharing them between the container
        and enterprise patched apps. Contributed to the overall design and
        the majority of coding done on iOS.
  % \item Improved the security and stability of the enterprise patched app
  %       feature on iOS.
  %       %By patching a custom dylib which performs all sorts of function hooking
  %       %it enables the secure container on many ordinary apps.
  %       Incorporated a secure and creative data sharing channel between the
  %       main container and patched apps by implementing a mini SSL like protocol
  %       over the pasteboard API.
  % \item Bullet-proofed the jailbreak detection feature by adding a runtime code
  %       signing signature check for any loaded Mach-O dylib's.
  \end{itemize}

  {\bf Software Engineer -- Silver Spring Networks}, Redwood City, CA USA\hfill Aug 2010 -- Jun 2012
  \vspace{.05in}
  \begin{itemize}
  \item Took major responsibilities in developing Nodesim - a network device
        simulation product for virtualizing smart grid devices in scale,
        during which I took initiatives in the design, implementation,
        quality control, maintenance, and knowledge transfer of the product.
  \item Practiced network programming in C/C++ on Linux platforms with a
        multi-process, request-driven approach, during which I gained
        experience in:
        \begin{itemize}
        \item implementing dual-stack IPv4/IPv6 server/client applications.
        \item virtualizing the network stack and protocol of smart grid devices
              in pure software by modifying the low-level C code from device
              firmware and linking them against high-level application code.
        \item employing packet sniffing and spoofing using raw sockets and
              libpcap, making the simulated traffic transparent to other
              integrated back office software.
%        \item deriving solutions from device specifications and RFCs with
%              little explicit instructions.
        \end{itemize}
%  \item Built a light and robust mini name server in C/C++ for managing
%        multiple instances of the simulation tool hosting on the same server.
% \item Worked part-time in the middle tier and back end of a multi-tier Java EE
%       web application which employs Spring, Tomcat, and Oracle. Incorporated
%       a feature for automatic schema migration between version upgrades.
% \item Invented a UDP traffic forwarder in Python using raw sockets for
%       multicasting packets as is to various destinations.
  \end{itemize}

%   \section{\sstyle Highlights of Coursework and Projects}
%   {\sl Programming Languages and Compilers}
% %  \vspace{.05in}
%   \begin{itemize}
%   \item Developed a dynamically typed interpreted language with extensions such
%         as coroutine and list comprehension; all based on a lexer, Earley parser
%         generator, and bytecode interpreter built from scratch.
% %  \item Implemented a simple HTML rendering engine by writing code in the
% %        language above to traverse the DOM generated from HTML by the parser
% %        generator.
%   \end{itemize}

%  {\sl Operating Systems and System Programming}
%  \vspace{.05in}
%  \begin{itemize}
%  \item Complemented the educational NachOS with a thread system,
%        multiprogramming support and system calls, virtual memory and
%        paging, and a simple network protocol similar to TCP/IP.
%  \end{itemize}

%  {\sl Introduction to Communication Networks}
%  \vspace{.05in}
%  \begin{itemize}
%  \item Implemented basic features of TCP with congestion control using
%        UDP and Java threads and synchronization.
%  \end{itemize}

% {\sl Efficient Algorithms and Intractable Problems}\hspace{.5in}
% {\sl Operating Systems and System Programming}\vspace{.05in}\\
% {\sl Intoduction to Communication Networks}\hspace{.82in}
% {\sl Introduction to Artificial Intelligence}\vspace{.05in}\\
% {\sl Foundations of Computer Graphics}\hspace{1.14in}
% {\sl Computer Architecture and Engineering}\vspace{.05in}\\

  \section{\sstyle Skills}
  \begin{description}
  \item[{\it Development:}] Scala, Ruby on Rails, AngularJS, D3.js, JavaScript,
    Bootstrap, Objective-C/iOS, Java, Python, C/C++, Linux, AWS, Git,
    Functional Programming.
  \item[{\it Technologies:}] Apache Spark, Elasticsearch, Cassandra, MongoDB,
    NoSQL, Big Data, MapReduce, GraphQL, REST, Akka, Kafka, ZeroMQ, ELK, Mobile,
    SaaS, Distributed Systems, Networking.
% \item[{\it Development:}] Objective-C/iOS, C/C++, Python, Java, Scheme, Bash, Linux, OpenSSL;
%   some experience with J2EE, Spring, Oracle, JavaScript, and Ajax;
%   OpenGL, PL/SQL, MIPS assembly, \LaTeX{}.
% \item[{\it Tools:}] Vim, Emacs, Xcode, Eclipse, Git, Perforce, SVN, gdb, make, ssh, tcpdump, JIRA, Scrum, etc.
  \item[{\it Languages:}] English, Cantonese, Mandarin.
  \end{description}

%  \section{\sstyle Personal}
%  US citizen

\end{resume}
\end{document}
